\documentclass[9pt,a4paper]{extarticle}
\include{structure}
\hyphenation{}
\begin{document}

\input{title}

\section*{Cover Letter – Frontend Engineer, Merchant Group}

I'm a software engineer with a strong interest in building clean, scalable, and maintainable systems — both in the frontend and backend. Over the past few years, I’ve worked on various products from digital banking apps to internal tools, and have led frontend architecture efforts for modular, micro-frontend-based platforms. I'm currently based in Finland and looking for a new opportunity where I can contribute to a team that values technical quality and thoughtful product development.

Most of my recent work has involved Vue.js, Node.js, and TypeScript. I’ve also worked with component libraries, micro-frontend setups, and design systems. While my main focus is frontend, I enjoy collaborating across the stack and have experience designing backend services with PostgreSQL, Redis, and messaging systems like RabbitMQ. I like teams where engineers have ownership across the full development lifecycle — from architecture to deployment and observability.

I’m particularly interested in this role because of the mix of technical ownership, collaboration, and product impact. I enjoy working on tools that empower others — whether it’s merchants, teammates, or internal users — and I try to bring a balance of pragmatism and care to my work.

Thanks for considering my application. I’d be happy to talk more and learn about the team.

\vspace{2em}
\noindent
Sincerely, \\
\noindent
Pedram Soofi

\end{document}