\headline{Experience}
    \setlength{\topsep}{0pt}
    \setlength{\partopsep}{0pt}
    \setlength{\itemsep}{0.1em}
    \setlength{\leftmargin}{0pt}
    \setlength{\itemindent}{0pt}
    \jobtitlewithcompany{Technical Team Lead | Senior Front-End Developer}{Jun 2023}{Sep 2025}{\href{https://www.linkedin.com/company/part-software/}{Part Software Group}}
    \begin{customitemize}
        \item Build a scalable Micro-Frontend ecosystem (Vite) and custom CI/CD publishing engine for a multi-tenant \href{https://set.postbank.ir/}{Digital Banking} platform, automating white-labeling and \textbf{accelerating client delivery speed by 20x}.
        \item Achieved \textbf{10x codebase scalability} by establishing a ``Shared Kernel'' repository and configurable Design System, utilizing \textbf{Clean Architecture} to centralize reusable business logic and enforce strict UI consistency across micro-apps.
        \item Engineered a secure, framework-agnostic State Machine to manage complex loan workflows with strict authorization guards,
utilizing an Event-Driven Architecture (Web Workers) for high-performance, decoupled service communication.
        \item Co-founded the Frontend Infrastructure Chapter to spearhead architectural modernization (DDD, FSD) and enforce SOLID principles, establishing a centralized UI library and \textbf{driving deep performance optimization}.
        \item Mentored +6 developers to elevate technical proficiency, fostering a high-performance culture through rigorous code reviews, algorithmic training, and collaborative knowledge sharing.
        \item Conducted advanced technical interviews to identify high-potential talent, rigorously assessing candidates on Clean Code, optimization, and soft skills to maintain high engineering standards.
     \end{customitemize}

    \noindent\jobtitlewithcompany{Front-End Developer}{Feb 2020}{Jun 2023}{\href{https://www.linkedin.com/company/part-software/}{Part Software Group}}
    \begin{customitemize}
 
   \item Engineered a high-performance authentication platform \href{https://farashenasa.ir/}{Farashenasa} serving \textbf{4M+ users}, utilizing \textbf{Clean Architecture} and \textbf{DDD} for scalability. Implemented a robust \textbf{WebRTC camera module} with background AI processing (Web Workers) for liveness detection, ensuring strict \textbf{WCAG accessibility} and security compliance.
    \item Developed a scalable, multi-tenant authentication widget \href{https://ekyc.isignal.ir/}{Ekyc} integrated by \textbf{20+ enterprise clients} (e.g., \href{https://snapp.isignal.ir/}{Snapp}, \href{https://mofid.isignal.ir/}{Mofid}, \href{https://farabi.isignal.ir/}{Farabi}). Designed a \textbf{configuration-driven architecture} served via iFrames, enabling seamless, customized embedding across high-traffic platforms without code duplication.
    \item Built \href{https://ivira.ai/}{Ivira} a comprehensive AI marketplace hosting \textbf{120+ services} with \textbf{SSR and PWA capabilities} for superior performance. Engineered a dynamic \textbf{Form Generator engine} that abstracted complex service inputs, \textbf{increasing development velocity by 10x} and ensuring maintainability.
    \item Delivered \textbf{20+ diverse web applications}, including a custom \textbf{TradingView engine fork}, an online \textbf{PDF Catalog Builder} for festivals, and a \textbf{Nuxt.js Static Site Generator} (Keystone CMS) that accelerated content delivery by \textbf{20x}.
    \item Enforced high engineering standards across all projects by implementing \textbf{comprehensive testing} strategies (Unit/E2E) and performance optimization techniques, ensuring highly maintainable, bug-free, and efficient codebases.
    \item Designed and led a structured \textbf{Internship Program} for \textbf{20+ candidates}, creating tailored learning paths focused on \textbf{Cloud-native frontend development} (Serverless). This initiative accelerated junior onboarding and significantly improved the company's engineering talent pipeline.
\end{customitemize}
    \vspace{0.5em}

    \noindent\jobtitlewithcompany{Front-End Engineer (Remote)}{Apr 2024}{Aug 2025}{\href{https://rahe-roshd.com}{Rahe Roshd Institute}}
    \begin{customitemize}
    \item Acted as a \textbf{System Analyst and Engineer} to architect a cohesive booking ecosystem (Client, Provider, Staff portals) serving \textbf{1,000+ daily customers}. Established a ``Shared Kernel'' and unified Design System to standardize UI across the three apps, achieving a \textbf{20x increase} in development velocity.
    \item Implemented a modular typescript architecture featuring a robust \textbf{ACL (Access Control List) layer}, ensuring secure, role-based feature access. Designed loosely-coupled UI modules to enable independent development and scalability without impacting core functionality.
    \item Adopted \textbf{Test-Driven Development (TDD)} and Agile/Scrum workflows to support a sensitive user base, partnering with product teams to ensure high UX quality, predictable releases, and minimized regressions.
    \end{customitemize}
 \vspace{0.5em}
